---
title: "Bayes Factor Design Analysis: Dynamic Report for Fixed-N Design"
output: pdf_document
classoption: a3paper
fontsize: 12pt
params:
  method.fixed: NA
  choiceBFdetails.fixed: NA
  true.ES.fixed: NA
  samplesize.fixed: NA
  decisionboundary.fixed: NA
  res: NA
  fixed.sim: NA
  analysis.expBF.list: NA
  analysis.expBF: NA
  probability.fixed: NA
  evidencestrength.fixed: NA
  samplesizeH0.fixed: NA
  NforBF.H0: NA
  NforBF.H1: NA
---

This is a dynamic report of your Bayes Factor Design Analysis for the fixed-N design. The analysis was conducted on `r I(print(as.character(Sys.time())))`.

# Selected parameters

**Samplesize:** `r params$samplesize.fixed`

**Data Generating Process:** ES = `r params$true.ES.fixed`

**Decision Boundaries:**

* Lower Boundary: `r 1/params$decisionboundary.fixed`
* Upper Boundary: `r params$decisionboundary.fixed`

**Prior on Effect Size:**

* Default Prior: Cauchy($\mu$ = 0, $r$ = $\sqrt{2}/2$)
* Informed Prior: t($\mu$ = 0.35, $r$ = 0.102, $df$ = 3)

# Analyses

`r if(length(params$choiceBFdetails.fixed) != 0) {"## Part 1: What Bayes factors can I expect?"}`

```{r fig.width=10, fig.height=5, echo=FALSE }

if ("BFdist" %in% params$choiceBFdetails.fixed){
  combine.plot.exp.BF.dist(method = params$method.fixed,
                                       res.H1 = params$fixed.sim[[params$res]],
                                       res.H0 = params$fixed.sim[["res.0"]],
                                       true.ES.H1 = params$true.ES.fixed,
                                       samplesize = params$samplesize.fixed,
                                       boundary = c(1/params$decisionboundary.fixed, params$decisionboundary.fixed))
  }
```

```{r echo=FALSE}
library(knitr)


# ---------------------------------------------------- Median Tables ---------------------------------------------------------------

if("MedBF" %in% params$choiceBFdetails.fixed){
    
    medBF.1.table.default <- params$analysis.expBF.list[[params$analysis.expBF]]$df.default %>% filter(n == params$samplesize.fixed) %>% select(quant.50) %>% exp(.)
    medBF.0.table.default <- params$analysis.expBF.list[["analysis.expBF.0"]]$df.default %>% filter(n == params$samplesize.fixed) %>% select(quant.50) %>% exp(.)
    medBF.table.default <- cbind(medBF.1.table.default, medBF.0.table.default)
    
    if("Default" %in% params$method.fixed){
      return(kable(medBF.table.default, col.names = c("Median Bayes Factor (Default)", "Median Bayes Factor (Default, H0)"), digits = 2, caption = "Medians of the Bayes Factor Distribution for the Default Prior"))
    }}


if ("MedBF" %in% params$choiceBFdetails.fixed){
    medBF.1.table.informed <- params$analysis.expBF.list[[params$analysis.expBF]]$df.informed %>% filter(n == params$samplesize.fixed) %>% select(quant.50) %>% exp(.)
    medBF.0.table.informed <- params$analysis.expBF.list[["analysis.expBF.0"]]$df.informed %>% filter(n == params$samplesize.fixed) %>% select(quant.50) %>% exp(.)
    medBF.table.informed <- cbind(medBF.1.table.informed, medBF.0.table.informed)

    if("Informed" %in% params$method.fixed){
      return(kable(medBF.table.informed, col.names = c("Median Bayes Factor (Informed)", "Median Bayes Factor (Informed, H0)"), digits = 2, caption = "Medians of the Bayes Factor Distribution for the Informed Prior"))
    }}

# ---------------------------------------------------- Quartile Tables -------------------------------------------------------------


if ("BFquantiles" %in% params$choiceBFdetails.fixed){
    
    BF.quantiles.1.table.def <- params$analysis.expBF.list[[params$analysis.expBF]]$df.default %>% filter(n == params$samplesize.fixed) %>% select(quant.05, quant.25, quant.75, quant.95) %>% exp(.)
    BF.quantiles.0.table.def <- params$analysis.expBF.list[["analysis.expBF.0"]]$df.default %>% filter(n == params$samplesize.fixed) %>% select(quant.05, quant.25, quant.75, quant.95) %>% exp(.)
    BF.quantiles.table.def <- cbind(c(paste0("H1: ES = ", params$true.ES.fixed), "H0: ES = 0"),rbind(BF.quantiles.1.table.def, BF.quantiles.0.table.def))

    if("Default" %in% params$method.fixed){
      return(kable(BF.quantiles.table.def, col.names = c("DGP", "5%", "25%", "75%", "95%"), caption = "Quantiles of the Bayes Factor Distribution (Default Prior on Effect Size)", digits = 2))
    }}

if ("BFquantiles" %in% params$choiceBFdetails.fixed){
    
    BF.quantiles.1.table.inf <- params$analysis.expBF.list[[params$analysis.expBF]]$df.informed %>% filter(n == params$samplesize.fixed) %>% select(quant.05, quant.25, quant.75, quant.95) %>% exp(.)
    BF.quantiles.0.table.inf <- params$analysis.expBF.list[["analysis.expBF.0"]]$df.informed %>% filter(n == params$samplesize.fixed) %>% select(quant.05, quant.25, quant.75, quant.95) %>% exp(.)
    BF.quantiles.table.inf <- cbind(c(paste0("H1: ES = ", params$true.ES.fixed), "H0: ES = 0"),rbind(BF.quantiles.1.table.inf, BF.quantiles.0.table.inf))

    if("Informed" %in% params$method.fixed){
      return(kable(BF.quantiles.table.inf, col.names = c("DGP", "5%", "25%", "75%", "95%"), caption = "Quantiles of the Bayes Factor Distribution (Informed Prior on Effect Size)", digits = 2))
    }}

# ---------------------------------------------------- Error Rates Tables ----------------------------------------------------------


type1error.table <- FPFN.fixed(params$fixed.sim[["res.0"]], params$method.fixed, params$decisionboundary.fixed, params$samplesize.fixed, 1)
      type2error.table <- FPFN.fixed(params$fixed.sim[[params$res]], params$method.fixed, params$decisionboundary.fixed, params$samplesize.fixed, 2)
      errors <- rbind(type1error.table, type2error.table)
      rownames(errors) <- c("False Positive Evidence Rates", "False Negative Evidence Rates")
      if(ncol(errors) == 1 & "Default" %in% params$method.fixed){colnames(errors) <- "Default Prior on ES"}
      if(ncol(errors) == 1 & "Informed" %in% params$method.fixed){colnames(errors) <- "Informed Prior on ES"}
    
    if("errorrates.fixedn" %in% params$choiceBFdetails.fixed & length(params$method.fixed) != 0){  
      return(kable(errors, row.names = TRUE, digits = 3, caption = "Rates of Misleading Evidence", col.names = colnames(errors)))}
```

\newpage

## Part 2: What sample size do I need to obtain a certain strength of evidence with a certain probability?

``` {r echo=FALSE}
# ---------------------------------------------------- Part II: N for BF -----------------------------------------------------------

text.default.H0 <- params$NforBF.H0[1]
text.informed.H0 <- params$NforBF.H0[2]
text.default.H1 <- params$NforBF.H1[1]
text.informed.H1 <- params$NforBF.H1[2]


    if("Default" %in% params$method.fixed & params$samplesizeH0.fixed == TRUE){
      HTML("<p style=font-size:15px >", paste0("If H0 is true and the default prior on effect size is used for analyses, ", text.default.H0, "</p>"))
    }
    
    if("Informed" %in% params$method.fixed & params$samplesizeH0.fixed == TRUE){
      HTML("<p style=font-size:15px >", paste0("If H0 is true and the informed prior on effect size is used for analyses, ", text.informed.H0, "</p>"))
    }
    
    if("Default" %in% params$method.fixed){
      HTML("<p style=font-size:15px >", paste0("If the effect size is ", params$true.ES.fixed, " and the default prior on effect size is used for analyses, ", text.default.H1, "</p>"))
    }

    if("Informed" %in% params$method.fixed){
      HTML("<p style=font-size:15px >", paste0("If the effect size is ", params$true.ES.fixed, " and the informed prior on effect size is used for analyses, ", text.informed.H1, "</p>"))
    }

```
