---
title: "Bayes Factor Design Analysis: Dynamic Report for Fixed-N Design"
output: pdf_document
classoption: a3paper
fontsize: 12pt
geometry: margin=2cm
params:
  true.ES: NA
  medians: NA
  bound: NA
  method: NA
  SummaryPlot: NA
  stats: NA
  FPFN: NA
  vioplot: NA
  bp: NA
  histogram: NA
  choicenames.hinges: NA
  choicenames.whisker: NA
  choicevalues: NA
  hinges: NA
  whiskers: NA
  efficiency: NA
  defaultmedian: NA
  informedmedian: NA
  n.default.H1: NA
  n.default.H0: NA
  n.informed.H1: NA
  n.informed.H0: NA
  ndistslist: NA
  efficiencylist: NA
  seq.simresults: NA
  tabdata: NA
  tabdata.0: NA
  BFDA.result: NA
                     
---

This is a dynamic report of your Bayes Factor Design Analysis for the sequential design. The analysis was conducted on `r I(print(as.character(Sys.time())))`.

# Selected parameters

**Prior on Effect Size:**

* Default Prior: Cauchy($\mu$ = 0, $r$ = $\sqrt{2}/2$)
* Informed Prior: t($\mu$ = 0.35, $r$ = 0.102, $df$ = 3)

**Data Generating Process:** ES = `r params$true.ES`

**Decision Boundaries:**

* Lower Boundary: `r round(1/as.numeric(params$bound), 2)`
* Upper Boundary: `r as.numeric(params$bound)`


```{r echo=FALSE, fig.height=5, fig.width=10}
efficiencyplot(params$efficiencylist[[params$efficiency]],
               params$true.ES,
               params$defaultmedian,
               params$informedmedian,
               params$hinges,
               params$whiskers
               )
```


```{r echo=FALSE, fig.width=10, fig.height=10}

if (length(params$SummaryPlot) > 0 & is.element("Default", params$method)){
      summaryplot.sequentialBFDA(SequentialBF.obsub = params$seq.simresults[[params$BFDA.result]], 
                                 boundary = as.numeric(params$bound),
                                 method = "default")
}

if (length(params$SummaryPlot) > 0 & is.element("Informed", params$method)){
     summaryplot.sequentialBFDA(SequentialBF.obsub = params$seq.simresults[[params$BFDA.result]],
                                boundary = as.numeric(params$bound),
                                method = "informed")
}
```

```{r echo=FALSE}
# -------------------------------------------- Median Tables -------------------------------------------------------------------
library(knitr)

if(is.element("medians", params$stats)){
      tab <- select(params$tabdata.0, starts_with("median"), boundary2.H0) %>% filter(boundary2.H0 == params$bound) %>% select(-boundary2.H0)
      colnames(tab) <- params$method
      return(kable(tab, caption = "Median N if H0 is true", digits = 0))
}
if(is.element("medians", params$stats)){
    tab <- select(params$tabdata, starts_with("median"), boundary2) %>% filter(boundary2 == params$bound) %>% select(-boundary2)
    colnames(tab) <- params$method
    return(kable(tab, caption = "Median N if H1 is true", digits = 0, align = "l"))
}


# ---------------------------------------- Hinges Tables ------------------------------------------------------------------------


if(is.element("hinges", params$stats)){
      tab <- select(params$tabdata.0, starts_with("lowhinge"), starts_with("uphinge"), boundary2.H0) %>% filter(boundary2.H0 == params$bound) %>% select(-boundary2.H0)
      if(ncol(tab) == 4){
        colnames(tab) <- c("Lower Hinge Default", "Lower Hinge Informed", "Upper Hinge Default", "Upper Hinge Informed")
      } else if (is.element("lowhinge.default", colnames(tab))){
        colnames(tab) <- c("Lower Hinge Default", "Upper Hinge Default")
      } else {
        colnames(tab) <- c("Lower Hinge Informed", "Upper Hinge Informed")
      }
      return(kable(tab, caption = "Hinges of N if H0 is true", digits = 0, align = "l"))
}

if(is.element("hinges", params$stats)){
      tab <- select(params$tabdata, starts_with("lowhinge"), starts_with("uphinge"), boundary2) %>% filter(boundary2 == params$bound) %>% select(-boundary2)
      if(ncol(tab) == 4){
        colnames(tab) <- c("Lower Hinge Default", "Lower Hinge Informed", "Upper Hinge Default", "Upper Hinge Informed")
      } else if (is.element("lowhinge.default", colnames(tab))){
        colnames(tab) <- c("Lower Hinge Default", "Upper Hinge Default")
      } else {
        colnames(tab) <- c("Lower Hinge Informed", "Upper Hinge Informed")
      }
      return(kable(tab, caption = "Hinges of N if H1 is true", digits = 0, align = "l"))
}

# ----------------------------------------------- Whiskers Table ------------------------------------------------------------------

if(is.element("whiskers", params$stats)){
      tab <- select(params$tabdata.0, starts_with("lowwhisk"), starts_with("upwhisk"), boundary2.H0) %>% filter(boundary2.H0 == params$bound) %>% select(-boundary2.H0)
      if(ncol(tab) == 4){
        colnames(tab) <- c("Lower Whisker Default", "Lower Whisker Informed", "Upper Whisker Default", "Upper Whisker Informed")
      } else if (is.element("lowhinge.default", colnames(tab))){
        colnames(tab) <- c("Lower Whisker Default", "Upper Whisker Default")
      } else {
        colnames(tab) <- c("Lower Whisker Informed", "Upper Whisker Informed")
      }
      return(kable(tab, caption = "Whiskers of N if H0 is true", digits = 0, align = "l"))
}

if(is.element("whiskers", params$stats)){
      tab <- select(params$tabdata, starts_with("lowwhisk"), starts_with("upwhisk"), boundary2) %>% filter(boundary2 == params$bound) %>% select(-boundary2)
      if(ncol(tab) == 4){
        colnames(tab) <- c("Lower Whisker Default", "Lower Whisker Informed", "Upper Whisker Default", "Upper Whisker Informed")
      } else if (is.element("lowhinge.default", colnames(tab))){
        colnames(tab) <- c("Lower Whisker Default", "Upper Whisker Default")
      } else {
        colnames(tab) <- c("Lower Whisker Informed", "Upper Whisker Informed")
      }
      return(kable(tab, caption = "Whiskers of N if H1 is true", digits = 0, align = "l"))
}


# --------------------------------- Quantile Tables -------------------------------------------------------------------------------


if(is.element("quartiles", params$stats) & is.element("Default", params$method)){
      tab.default <- select(params$tabdata.0, starts_with("quant"), boundary2.H0) %>% filter(boundary2.H0 == params$bound) %>% select(-boundary2.H0) %>% select(ends_with("default.H0"))
      if(ncol(tab.default) > 0){colnames(tab.default) <- c("5%", "25%", "75%", "95%")}
      return(kable(tab.default, caption = "Relevant Quantiles of the Distribution of N (DGP: H0, Default Prior on Effect Size)", digits = 0, align = "l"))
}

if(is.element("quartiles", params$stats) & is.element("Informed", params$method)){
      tab.informed <- select(params$tabdata.0, starts_with("quant"), boundary2.H0) %>% filter(boundary2.H0 == params$bound) %>% select(-boundary2.H0) %>% select(ends_with("informed.H0"))
      if(ncol(tab.informed) > 0){colnames(tab.informed) <- c("5%", "25%", "75%", "95%")}
      return(kable(tab.informed, caption = "Relevant Quantiles of the Distribution of N (DGP: H0, Informed Prior on Effect Size)", digits = 0, align = "l"))
}

if(is.element("quartiles", params$stats) & is.element("Default", params$method)){
      tab.default <- select(params$tabdata, starts_with("quant"), boundary2) %>% filter(boundary2 == params$bound) %>% select(-boundary2) %>% select(ends_with("default"))
      if(ncol(tab.default) > 0){colnames(tab.default) <- c("5%", "25%", "75%", "95%")}
      
      return(kable(tab.default, caption = "Relevant Quantiles of the Distribution of N (DGP: H1, Default Prior on Effect Size)", digits = 0, align = "l"))
}

if(is.element("quartiles", params$stats) & is.element("Informed", params$method)){
      tab.informed <- select(params$tabdata, starts_with("quant"), boundary2) %>% filter(boundary2 == params$bound) %>% select(-boundary2) %>% select(ends_with("informed"))
      if(ncol(tab.informed) > 0){colnames(tab.informed) <- c("5%", "25%", "75%", "95%")}

      return(kable(tab.informed, caption = "Relevant Quantiles of the Distribution of N (DGP: H1, Informed Prior on Effect Size)", digits = 0, align = "l"))
}

# ------------------------------------------------- Error Rates ------------------------------------------------------------------

if (is.element("H0", params$FPFN)){
      errors <- select(params$tabdata.0, starts_with("upper.hit"), boundary2.H0) %>% filter(boundary2.H0 == params$bound) %>% select(-boundary2.H0)
      if(ncol(errors) == 2){
        colnames(errors) <- c("Default Prior on Effect Size", "Informed Prior on Effect Size")
      } else if (is.element("lower.hit.default", colnames(errors))) {
        colnames(errors) <- "Default Prior on Effect Size"
      } else {
        colnames(errors) <- "Informed Prior on Effect Size"
      }
      return(kable(errors, caption = "False Positive Error Rates", align = "l"))
}

if (is.element("H1", params$FPFN)){
      errors <- select(params$tabdata, starts_with("lower.hit"), boundary2) %>% filter(boundary2 == params$bound) %>% select(-boundary2)
      if(ncol(errors) == 2){
        colnames(errors) <- c("Default Prior on Effect Size", "Informed Prior on Effect Size")
      } else if (is.element("lower.hit.default", colnames(errors))) {
        colnames(errors) <- "Default Prior on Effect Size"
      } else {
        colnames(errors) <- "Informed Prior on Effect Size"
      }
      return(kable(errors, caption = "False Negative Error Rates", align = "l"))
}

```

```{r echo=FALSE, fig.height=5, fig.width=10}

if(length(params$vioplot) > 0){
      cleanviolinplot(params$ndistslist,
                      true.ES = params$true.ES,
                      bound = params$bound,
                      default = is.element("Default", params$method),
                      informed = is.element("Informed", params$method),
                      H0 = is.element("H0", params$vioplot),
                      H1 = is.element("H1", params$vioplot))
}

if(length(params$bp) > 0){
      cleanboxplot(params$ndistslist,
                    true.ES = params$true.ES,
                    bound = params$bound,
                    default = is.element("Default", params$method),
                    informed = is.element("Informed", params$method),
                    H0 = is.element("H0", params$bp),
                    H1 = is.element("H1", params$bp))
}

if(length(params$histogram) > 0){
      cleanhist.combine(true.ES = params$true.ES,
                        n.default.H1 = params$n.default.H1[,1],
                        n.default.H0 = params$n.default.H0[,1],
                        n.informed.H1 = params$n.informed.H1[,1],
                        n.informed.H0 = params$n.informed.H0[,1],
                        default = is.element("Default", params$method),
                        informed = is.element("Informed", params$method),
                        H0 = is.element("H0", params$histogram),
                        H1 = is.element("H1", params$histogram)
                        )
}

```